Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated References
Also added contact email.

\title*{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)} 
\titlerunning{Animal Life Cycle Algorithm (ALCA)}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{J. C. Felix-Saul, Mario García Valdez}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}
\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

            Based on the historically best candidate
            solution and the elite set, we use the Golden Ratio (shown in
            Figure~\ref{fig.golden_ratio}) to compute the distance between new individuals
            in the population, making an improved distribution. It randomly selects a
            solution from the elite set and uses the Golden Ratio to compute multiple
            solutions against the best-found candidate.

>>>>

\title*{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)} 
\titlerunning{Animal Life Cycle Algorithm (ALCA)}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{J. C. Felix-Saul, Mario García Valdez}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{jose.felix201@tectijuana.edu.mx}
\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{mario@tectijuana.edu.mx}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

            Based on the historically best candidate
            solution and the elite set, we use the Golden Ratio (shown in
            Figure~\ref{fig.golden_ratio}) to compute the distance between new individuals
            in the population, making an improved distribution. It randomly selects a
            solution from the elite set and uses the Golden Ratio 
            \cite{nematollahi2020novel, gaikwad2021face, khesin2022golden, sym13081334, https://doi.org/10.1111/nyas.14895} 
            to compute multiple solutions against the best-found candidate.
